PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$

### 2014-12-19 qfenv_paper/qf_environment.tex
mike intro edit

Observations such as \cite{Weinmann:2006aa} and \cite{Peng:2010aa} credit some of these proposed internal processes for the cessation of star-formation, especially in massive galaxies. Meanwhile, observations of galaxy properties such as color and morphology correlating with environment suggest that environment may play a role in ceasing star-formation (\citealt{blanton09a} and references therein). However, it remains to be discerned whether these trends reflect the underlying differences among galaxy populations in different environments or if they are in fact effects of environment dependent external processes, which cause galaxies that would otherwise continue forming stars to cease their star-formation.

>>>>

Observations such as \cite{Weinmann:2006aa} and \cite{Peng:2010aa} credit some of these proposed internal processes for the cessation of star-formation, especially in massive galaxies. Meanwhile, observations of galaxy properties such as color and morphology correlating with environment suggest that environment may play a role in ceasing star-formation (\citealt{blanton09a} and references therein). However, it remains to be determined whether the environmental trends in galaxy properties reflect the direct effect of external environment on the galaxies' evolution (e.g. ram pressure, tidal forces, mergers) or reflect statistical differences in the histories of galaxies in different environments (e.g. an earlier formation time in dense regions).

%However, it remains to be discerned whether these trends reflect the underlying differences among galaxy populations in different environments or if they are in fact effects of environment dependent external processes, which cause galaxies that would otherwise continue forming stars to cease their star-formation.
